### 2017-11-01 submission/manuscript.Rmd
complete addition of last result section

***Using the Whole Community Increases Model AUC:***
For both fecal and tissue samples (matched and unmatched) there was a decrease in AUC when only OTUs from the CRC associated genera are used [Figure 4 & 5]. This decrease is observed in both adenoma and carcinoma groups [Figure 4 & 5]. The genus models generally had similar trends as observed for the OTU based models with the full genera models performing better then the CRC associated genera models [Figure S4-S4]. Both genus models perform similarily in their ability to be able to predict lesion (adenoma or carcinoma) with carcinoma having a higher AUC then adenoma [Figure S6-S8]. Matched tissue samples for those with carcinoma had an AUC that was more similar to the adenoma models [Figure S6A, S7B, & S8] then carcinoma models [Figure S6B & S7A].

***Section 4***

>>>>

***Using the Whole Community Increases Model AUC:***
For both fecal and tissue samples (matched and unmatched) there was a decrease in AUC when only OTUs from the CRC associated genera are used [Figure 4 & 5]. This decrease is observed in both adenoma and carcinoma groups [Figure 4 & 5]. The genus models generally had similar trends as observed for the OTU based models with the full genera models performing better then the CRC associated genera models [Figure S4-S5]. Both genus models perform similarily in their ability to be able to predict lesion (adenoma or carcinoma) with carcinoma having a higher AUC then adenoma [Figure S6-S8]. Matched tissue samples for those with carcinoma had an AUC that was more similar to the adenoma models [Figure S6A, S7B, & S8] then carcinoma models [Figure S6B & S7A].

***Majority of Studies are Underpowered for Detecting Small Effect Size Differences:***
When assessing the power of each study at different effect sizes the majority of studies for both adenoma and carcinoma have an 80% power to detect a 30% difference [Figure 6A & B]. No single study that was analyzed had the standard 80% power to detect a difference that was eqaul to or below 10% [Figure 6A & B].  In order to achieve adequate power for small effect sizes it would be necessary to recruit over 1000 individuals for each arm of the study [Figure 6C].

### 2017-11-01 submission/manuscript.tex
complete addition of last result section

\textbf{\emph{Using the Whole Community Increases Model AUC:}} For both
fecal and tissue samples (matched and unmatched) there was a decrease in
AUC when only OTUs from the CRC associated genera are used {[}Figure 4
\& 5{]}. This decrease is observed in both adenoma and carcinoma groups
{[}Figure 4 \& 5{]}. The genus models generally had similar trends as
observed for the OTU based models with the full genera models performing
better then the CRC associated genera models {[}Figure S4-S4{]}. Both
genus models perform similarily in their ability to be able to predict
lesion (adenoma or carcinoma) with carcinoma having a higher AUC then
adenoma {[}Figure S6-S8{]}. Matched tissue samples for those with
carcinoma had an AUC that was more similar to the adenoma models
{[}Figure S6A, S7B, \& S8{]} then carcinoma models {[}Figure S6B \&
S7A{]}.

\textbf{\emph{Section 4}}

>>>>

\textbf{\emph{Using the Whole Community Increases Model AUC:}} For both
fecal and tissue samples (matched and unmatched) there was a decrease in
AUC when only OTUs from the CRC associated genera are used {[}Figure 4
\& 5{]}. This decrease is observed in both adenoma and carcinoma groups
{[}Figure 4 \& 5{]}. The genus models generally had similar trends as
observed for the OTU based models with the full genera models performing
better then the CRC associated genera models {[}Figure S4-S5{]}. Both
genus models perform similarily in their ability to be able to predict
lesion (adenoma or carcinoma) with carcinoma having a higher AUC then
adenoma {[}Figure S6-S8{]}. Matched tissue samples for those with
carcinoma had an AUC that was more similar to the adenoma models
{[}Figure S6A, S7B, \& S8{]} then carcinoma models {[}Figure S6B \&
S7A{]}.

\textbf{\emph{Majority of Studies are Underpowered for Detecting Small
Effect Size Differences:}} When assessing the power of each study at
different effect sizes the majority of studies for both adenoma and
carcinoma have an 80\% power to detect a 30\% difference {[}Figure 6A \&
B{]}. No single study that was analyzed had the standard 80\% power to
detect a difference that was eqaul to or below 10\% {[}Figure 6A \&
B{]}. In order to achieve adequate power for small effect sizes it would
be necessary to recruit over 1000 individuals for each arm of the study
{[}Figure 6C{]}.
